Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-08-27 analysis/exp2_analysis.Rmd
added some initial model data for 2AFC experiment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(here)
require(tidyverse)
require(tidyboot)

raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)
# row 1 is empty, row 2 should be header
d = raw[4:nrow(raw),]
names(d) = raw[2,]
d[,"NA"] = NULL
# duplicate column names
#names(d)[13]
#names(d)[21]

>>>>

```{r libraries}
knitr::opts_chunk$set(echo = TRUE)

require(here)
require(tidyverse)
require(tidyboot)
```

```{r load-model-data, include=F}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")

names(mdat)
mdat <- mdat %>% mutate(
    train_stage = cut_number(model_train_steps, 2),
    chose_target = ifelse(choice==target, 1, 0)
  )

mdat %>% group_by(drop, target, train_stage) %>% # alt, 
  summarize(chose_target=mean(chose_target), n=n()) %>%
  ggplot(aes(x=train_stage, y=chose_target, group=target, color=target)) + 
  facet_wrap(.~ drop) + 
  geom_point(aes(size=n)) + geom_line() + theme_bw() + ylim(0,1)

mdat %>% distinct(drop, target, alt)
```

```{r load-human-data, include=FALSE}
raw = read.csv2("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv", sep=',', header=F, stringsAsFactors = F)
# row 1 is empty, row 2 should be header
d = raw[4:nrow(raw),]
names(d) = raw[2,]
d[,"NA"] = NULL
# duplicate column names
#names(d)[13]
#names(d)[21]
